Glasshouse experiment

### 2018-02-20 experiment_info.Rmd
Updating plots

@@

```{r}

@@

Ovules

>>>>

Flower selection criteria: Big flowers, easy/fast growing.

@@

**Ovules**

```{r, echo=FALSE}

#OVYLE NUMBER OF THE DIFFERENT SPECIES N=15

library(reshape2)

# Consider NA's as 0, I have to double check this

ovules <- read.csv("Ovules.csv", sep=";")

#plot(ovules)

mean_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = mean, data = ovules, na.rm= TRUE)

colnames(mean_ovule)[2] <- "avg"

sd_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = sd, data = ovules, na.rm= TRUE)

colnames(sd_ovule)[2] <- "sdev"

x <- 1:8

plot(x, mean_ovule$avg,
     ylim=range(c(mean_ovule$avg-sd_ovule$sdev, mean_ovule$avg+sd_ovule$sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="N of Ovules")
# hack: we draw arrows but with very special "arrowheads"
arrows(x, mean_ovule$avg-sd_ovule$sdev, x, mean_ovule$avg+sd_ovule$sdev, length=0.05, angle=90, code=3)

axis(x, at=1:8, labels = mean_ovule$Species,cex=0.2, tick = FALSE, padj= -0.5, side = 1)

**Seed set Petunia**

```{r, echo=FALSE}
library(reshape2)

# Consider NA's as 0, I have to double check this

seed_set <- read.csv("PEIN_seed_set.csv", sep=";")

#Delete Cross with lost seeds
seed_set[c(12,17,19),4] <- NA
#Deleted

mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = seed_set, na.rm= TRUE)

mean_seed_seet$.-> avg

sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = seed_set, na.rm= TRUE)

sd_seed_seet$. -> sdev

sdev[4] <- 0

#plot(seed_set, cex.axis=0.5)

x <- 1:7

plot(x, avg,
     ylim=range(c(avg-sdev, avg+sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="PEIN seed set"
)
# hack: we draw arrows but with very special "arrowheads"
arrows(x, avg-sdev, x, avg+sdev, length=0.05, angle=90, code=3)

axis(x, at=1:7, labels = mean_seed_seet$Treatment,cex.axis=0.8, tick = FALSE, padj= -0.5, side = 1)

@@
